\documentclass[9pt,letterpaper]{article}

\usepackage[margin=0.54in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}

% ATS-friendly unicode mapping (pdfTeX only; XeTeX via Tectonic does not use this)
\ifdefined\pdfgentounicode
  \input{glyphtounicode}
  \pdfgentounicode=1
\fi

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\pagenumbering{gobble}
\urlstyle{same}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{4pt}{2pt}

\newcommand{\resumeHeader}[1]{%
  \begin{center}
    \vspace{1pt}
    {\fontsize{17pt}{19pt}\selectfont\bfseries #1\par}
    \vspace{3pt}
  \end{center}
}
\newcommand{\role}[4]{\textbf{#1} \hfill #2 \\
\textit{#3} \hfill \textit{#4}\\[-5pt]}

\begin{document}

\resumeHeader{Mutahhar BM - Full-Stack Engineer}
\begin{center}
\fontsize{9pt}{11pt}\selectfont
\href{mailto:mutahharbinmuzaffar@gmail.com}{mutahharbinmuzaffar@gmail.com} \;|\; +92 301 2498730 \;|\;
\href{https://www.linkedin.com/in/mutahhar-bin-muzaffar}{linkedin.com/in/mutahhar-bin-muzaffar} \;|\;
\href{https://github.com/bmutahhar}{github.com/bmutahhar}
\end{center}

\section*{Summary}
Full-Stack Engineer with 5+ years of experience building web products with JavaScript/TypeScript, Next.js, and Node.js. Brings 3+ years of Python scripting experience from freelance automation work and hands-on delivery of large React-to-Next.js migrations.

\section*{Experience}
\role{Senior Software Engineer}{Jul 2023 -- Present}{\href{https://www.imagine.art/}{\textbf{\underline{ImagineArt}}} - Vyro.ai}{Islamabad, Pakistan}
\begin{itemize}[leftmargin=*, itemsep=0pt, topsep=0pt, partopsep=0pt, parsep=0pt, after=\vspace{1pt}]
  \item Increased product adoption by leading \href{https://www.imagine.art/flow}{\textbf{\underline{Workflows}}} from ideation to MVP and architecting a unified React Flow canvas for text, image, and video generation.
  \item Increased team delivery capacity by onboarding and mentoring 4--5 engineers and setting implementation standards for real-time node orchestration.
  \item Increased rollout efficiency by 60\% and reduced access-update overhead by 35\% by implementing Firebase Remote Config feature gating, contributing to 20\% subscription growth.
  \item Led migration of a large React application surface to Next.js, improving long-term maintainability and enabling faster feature delivery on a modern TypeScript stack.
  \item Owned end-to-end delivery of the company blog using Next.js and Strapi CMS, improving content delivery reliability.

\end{itemize}

\role{Full Stack Developer}{Mar 2022 -- Mar 2025}{\href{https://www.engiselle.com/}{\textbf{\underline{Engiselle}}}}{Singapore}
\begin{itemize}[leftmargin=*, itemsep=0pt, topsep=0pt, partopsep=0pt, parsep=0pt, after=\vspace{1pt}]
  \item Increased transaction volume by \textbf{20\%} by delivering production eCommerce products for online pharmacy and home-repair marketplaces.
  \item Improved data-layer reliability by owning PostgreSQL-backed workflows and implementing ORM layers with Sequelize and Prisma for eCommerce and LMS products.
  \item Improved production stability and secure team access by deploying backend services on AWS EC2, managing PostgreSQL on Amazon RDS, and configuring S3/IAM controls.
  \item Increased user engagement by \textbf{35\%} by implementing real-time event notification workflows with Socket.io.
  \item Automated recurring operational workflows with Python scripting across freelance and product contexts, reducing repetitive manual work.
\end{itemize}

\role{Software Engineer}{Jun 2022 -- Jun 2023}{\href{https://www.devsinc.com/}{\textbf{\underline{DevsInc}}}}{Islamabad, Pakistan}
\begin{itemize}[leftmargin=*, itemsep=0pt, topsep=0pt, partopsep=0pt, parsep=0pt, after=\vspace{1pt}]
  \item Improved care-team workflow coverage by shipping healthcare product features with React, Material UI, scheduling workflows, and Twilio video integrations.
  \item Improved API flexibility and frontend-backend delivery speed by implementing GraphQL queries and mutations across a React frontend and NestJS backend for VeVe.
  \item Expanded mobile product reach by contributing React Native and Expo features that extended core VeVe workflows to cross-platform app experiences.
  \item Reduced load time by \textbf{40\%}, accelerated release cycles by \textbf{20\%}, and reduced support tickets by \textbf{30\%} by improving UX architecture and resolving 50+ production issues.
\end{itemize}

\role{Software Engineer}{Oct 2021 -- Jun 2022}{Pakistan Air Force}{Islamabad, Pakistan}
\begin{itemize}[leftmargin=*, itemsep=0pt, topsep=0pt, partopsep=0pt, parsep=0pt, after=\vspace{1pt}]
  \item Reduced deployment time by \textbf{50\%} while supporting \textbf{99.9\%} uptime by conducting 10+ feasibility studies and deploying 20+ Dockerized services on Kubernetes.
\end{itemize}

\section*{Education}
\textbf{Bachelor of Computer Science} \hfill 2021 \\
COMSATS University, Islamabad \hfill CGPA: 3.73/4.00

\section*{Skills}
\textbf{Languages:} JavaScript, TypeScript, Python, HTML, CSS/SCSS \\
\textbf{Frontend/Mobile:} React, Next.js, React Native, Expo, Tailwind CSS, ShadCN, Radix UI, Redux, Zustand \\
\textbf{Backend/Data/Infra:} Node.js, Express.js, NestJS, GraphQL, PostgreSQL, Prisma, Sequelize, Firebase, AWS (EC2, RDS, S3, IAM), Socket.io, Docker, Kubernetes, Strapi CMS \\
\textbf{Product/Delivery:} Full-Stack Development, eCommerce Workflows, AI Product Features, Performance Optimization, System Design, Scalable UI Patterns, Cross-Functional Delivery, Jest, Git, REST APIs

\end{document}
