\documentclass[9pt,letterpaper]{article}

\usepackage[margin=0.56in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}

% ATS-friendly unicode mapping (pdfTeX only; XeTeX via Tectonic does not use this)
\ifdefined\pdfgentounicode
  \input{glyphtounicode}
  \pdfgentounicode=1
\fi

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\pagenumbering{gobble}
\urlstyle{same}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{5pt}{3pt}

\newcommand{\resumeHeader}[1]{%
  \begin{center}
    \vspace{2pt}
    {\fontsize{18pt}{20pt}\selectfont\bfseries #1\par}
    \vspace{4pt}
  \end{center}
}
\newcommand{\role}[4]{\textbf{#1} \hfill #2 \\
\textit{#3} \hfill \textit{#4}\\[-4pt]}

\begin{document}

\resumeHeader{Mutahhar BM - Senior Fullstack Engineer}
\begin{center}
\fontsize{9pt}{11pt}\selectfont
\href{mailto:mutahharbinmuzaffar@gmail.com}{mutahharbinmuzaffar@gmail.com} \;|\; +92 301 2498730 \;|\;
\href{https://www.linkedin.com/in/mutahhar-bin-muzaffar}{linkedin.com/in/mutahhar-bin-muzaffar} \;|\;
\href{https://github.com/bmutahhar}{github.com/bmutahhar}
\end{center}

\section*{Summary}
Senior Fullstack Engineer with 5+ years of experience building production web products with TypeScript, React, Node.js, and NestJS. Delivers scalable REST and GraphQL APIs, owns frontend architecture, and ships reliable releases through Git workflows and cloud deployment pipelines.

\section*{Experience}
\role{Senior Software Engineer}{Jul 2023 -- Present}{\href{https://www.imagine.art/}{\textbf{\underline{ImagineArt}}} - Vyro.ai}{Islamabad, Pakistan}
\begin{itemize}[leftmargin=*, itemsep=0pt, topsep=0pt, partopsep=0pt, parsep=0pt, after=\vspace{2pt}]
  \item Product adoption increased by leading \href{https://www.imagine.art/flow}{\textbf{\underline{Workflows}}} from ideation to MVP and architecting a unified React Flow canvas for text, image, and video generation.
  \item Team delivery capacity increased by onboarding and mentoring 4--5 engineers and setting implementation standards for complex real-time node orchestration.
  \item Rollout speed improved by 60\% and access-update overhead dropped by 35\% by implementing Firebase Remote Config feature gating, contributing to 20\% subscription growth.
  \item Release consistency improved by setting Git-based team workflows and maintaining a Vercel deployment pipeline for a microfrontend architecture.
  \item Delivery predictability improved by partnering with product and design teams to scope high-impact work into clear engineering milestones.
\end{itemize}

\role{Full Stack Developer}{Mar 2022 -- Mar 2025}{\href{https://www.engiselle.com/}{\textbf{\underline{Engiselle}}}}{Singapore}
\begin{itemize}[leftmargin=*, itemsep=0pt, topsep=0pt, partopsep=0pt, parsep=0pt, after=\vspace{2pt}]
  \item Transaction volume increased by \textbf{20\%} by delivering production eCommerce products for online pharmacy and home-repair marketplaces.
  \item Data-layer reliability improved by owning PostgreSQL-backed data models and query flows with Sequelize and Prisma for eCommerce and LMS backends.
  \item Production operations improved by deploying Node.js backend services on AWS EC2, managing PostgreSQL on Amazon RDS, and configuring S3 bucket policies with IAM controls.
  \item User engagement increased by \textbf{35\%} by implementing real-time event notification workflows with Socket.io.
\end{itemize}

\role{Software Engineer}{Jun 2022 -- Jun 2023}{\href{https://www.devsinc.com/}{\textbf{\underline{DevsInc}}}}{Islamabad, Pakistan}
\begin{itemize}[leftmargin=*, itemsep=0pt, topsep=0pt, partopsep=0pt, parsep=0pt, after=\vspace{2pt}]
  \item API flexibility improved by implementing and consuming GraphQL queries and mutations across a React frontend and NestJS backend for VeVe.
  \item Care-team workflow efficiency improved by shipping healthcare dashboard features with React, Material UI, scheduling workflows, and Twilio video integrations.
  \item Expanded mobile workflow coverage by contributing React Native and Expo features that extended core VeVe product flows.
  \item Reduced load time by \textbf{40\%}, accelerated release cycles by \textbf{20\%}, and reduced support tickets by \textbf{30\%} by improving UX architecture and resolving 50+ production issues.
\end{itemize}

\role{Software Engineer}{Oct 2021 -- Jun 2022}{Pakistan Air Force}{Islamabad, Pakistan}
\begin{itemize}[leftmargin=*, itemsep=0pt, topsep=0pt, partopsep=0pt, parsep=0pt, after=\vspace{2pt}]
  \item Reduced deployment time by \textbf{50\%} while supporting \textbf{99.9\%} uptime by conducting 10+ feasibility studies and deploying 20+ Dockerized services on Kubernetes.
\end{itemize}

\section*{Education}
\textbf{Bachelor of Computer Science} \hfill 2021 \\
COMSATS University, Islamabad \hfill CGPA: 3.73/4.00

\section*{Skills}
\textbf{Languages:} JavaScript, TypeScript, HTML, CSS/SCSS, SQL \\
\textbf{Frontend/Mobile:} React, Next.js, React Native, Expo, Tailwind CSS, ShadCN, Radix UI, Redux, Zustand \\
\textbf{Backend/Data/Infra:} Node.js, Express.js, NestJS, REST APIs, GraphQL APIs, PostgreSQL, Prisma, Sequelize, Firebase (NoSQL), AWS (EC2, RDS, S3, IAM), Socket.io, Docker, Kubernetes, Strapi CMS \\
\textbf{Delivery/Architecture:} Git, Git workflows, CI/CD pipelines (Vercel), Fullstack System Design, Frontend Architecture, Performance Optimization, Scalable UI Patterns, Cross-Functional Delivery, Jest

\end{document}
