\documentclass[9pt,letterpaper]{article}

\usepackage[margin=0.58in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}

% ATS-friendly unicode mapping (pdfTeX only; XeTeX via Tectonic does not use this)
\ifdefined\pdfgentounicode
  \input{glyphtounicode}
  \pdfgentounicode=1
\fi

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\pagenumbering{gobble}
\urlstyle{same}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{7pt}{4pt}

\newcommand{\resumeHeader}[1]{%
  \begin{center}
    \vspace{2pt}
    {\fontsize{18pt}{20pt}\selectfont\bfseries #1\par}
    \vspace{4pt}
  \end{center}
}
\newcommand{\role}[4]{\textbf{#1} \hfill #2 \\
\textit{#3} \hfill \textit{#4}\\[-4pt]}

\begin{document}

\resumeHeader{Mutahhar BM - Product Engineer}
\begin{center}
\fontsize{9pt}{11pt}\selectfont
\href{mailto:mutahharbinmuzaffar@gmail.com}{mutahharbinmuzaffar@gmail.com} \;|\; +92 301 2498730 \;|\;
\href{https://www.linkedin.com/in/mutahhar-bin-muzaffar}{linkedin.com/in/mutahhar-bin-muzaffar} \;|\;
\href{https://github.com/bmutahhar}{github.com/bmutahhar}
\end{center}

\section*{Summary}
Product Engineer with 5+ years of full-stack experience shipping user-facing features across AI-assisted experiences, SaaS, and eCommerce. Builds with React, TypeScript, Node.js, PostgreSQL, and AWS while owning delivery from architecture through production rollout.

\section*{Experience}
\role{Senior Software Engineer}{Jul 2023 -- Present}{\href{https://www.imagine.art/}{\textbf{\underline{ImagineArt}}} - Vyro.ai}{Islamabad, Pakistan}
\begin{itemize}[leftmargin=*, itemsep=0pt, topsep=0pt, partopsep=0pt, parsep=0pt, after=\vspace{2pt}]
  \item Led \href{https://www.imagine.art/flow}{\textbf{\underline{Workflows}}} from ideation to MVP as a founding engineer, defining a unified React Flow canvas for text, image, and video generation.
  \item Expanded team execution by onboarding and mentoring 4--5 engineers and setting implementation direction for complex real-time node orchestration.
  \item Improved release consistency by establishing Git-based team workflows and maintaining a Vercel deployment pipeline for microfrontend releases across independently deployed modules.
  \item Improved rollout speed by 60\% and reduced access-update overhead by 35\% by implementing Firebase Remote Config feature gating, contributing to 20\% subscription growth.
  \item Partnered with product and design stakeholders to scope complex features into clear delivery milestones.

\end{itemize}

\role{Full Stack Developer}{Mar 2022 -- Mar 2025}{\href{https://www.engiselle.com/}{\textbf{\underline{Engiselle}}}}{Singapore}
\begin{itemize}[leftmargin=*, itemsep=0pt, topsep=0pt, partopsep=0pt, parsep=0pt, after=\vspace{2pt}]
  \item Increased transaction volume by \textbf{20\%} by delivering production eCommerce platforms for online pharmacy and home-repair workflows.
  \item Improved production reliability by deploying backend services on AWS EC2, managing PostgreSQL on Amazon RDS, and configuring S3 bucket policies with IAM-based team access controls.
  \item Improved backend data consistency by owning PostgreSQL query flows and implementing ORM layers with Sequelize and Prisma across eCommerce and LMS products.
  \item Increased user engagement by \textbf{35\%} by implementing real-time event notification workflows with Socket.io.
  \item Built AI-assisted voice and avatar learning interactions in a Next.js LMS by integrating Azure AI Speech text-to-speech and real-time avatar synthesis.
\end{itemize}

\role{Software Engineer}{Jun 2022 -- Jun 2023}{\href{https://www.devsinc.com/}{\textbf{\underline{DevsInc}}}}{Islamabad, Pakistan}
\begin{itemize}[leftmargin=*, itemsep=0pt, topsep=0pt, partopsep=0pt, parsep=0pt, after=\vspace{2pt}]
  \item Built and shipped a healthcare provider dashboard using React, Material UI, scheduling workflows, and Twilio video integrations.
  \item Improved API flexibility by implementing and consuming GraphQL queries and mutations across a React frontend and NestJS backend on the VeVe project.
  \item Improved release confidence and regression safety by implementing frontend unit tests with Jest and React Testing Library on the Kudo project.
  \item Improved dashboard UX and query performance, reducing load time by \textbf{40\%} and accelerating feature releases by \textbf{20\%}.
\end{itemize}

\role{Software Engineer}{Oct 2021 -- Jun 2022}{Pakistan Air Force}{Islamabad, Pakistan}
\begin{itemize}[leftmargin=*, itemsep=0pt, topsep=0pt, partopsep=0pt, parsep=0pt, after=\vspace{2pt}]
  \item Conducted 10+ feasibility studies in an R\&D team and developed geospatial interfaces with Mapbox; deployed 20+ Docker images on local Kubernetes, reducing deployment time by \textbf{50\%} while supporting \textbf{99.9\%} uptime.
\end{itemize}

\section*{Education}
\textbf{Bachelor of Computer Science} \hfill 2021 \\
COMSATS University, Islamabad \hfill CGPA: 3.73/4.00

\section*{Skills}
\textbf{Languages:} JavaScript, TypeScript, HTML, CSS/SCSS \\
\textbf{Frontend:} React, Next.js, Tailwind CSS, ShadCN, Radix UI, Redux, Zustand \\
\textbf{Backend/Data/Infra:} Node.js, Express.js, NestJS, GraphQL, PostgreSQL, Prisma, Sequelize, Firebase, AWS (EC2, RDS, S3, IAM), Socket.io, Docker, Kubernetes, Strapi CMS \\
\textbf{Quality/Delivery:} Jest, React Testing Library, Git, CI/CD (Vercel), Microfrontend Delivery, Performance Optimization, Scalable UI Patterns, REST APIs

\section*{Achievement}
Received the Bar Riser Award at Vyro in 2025 for contributions and sustained effort.

\end{document}
