\documentclass[9pt,letterpaper]{article}

\usepackage[margin=0.58in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}

% ATS-friendly unicode mapping (pdfTeX only; XeTeX via Tectonic does not use this)
\ifdefined\pdfgentounicode
  \input{glyphtounicode}
  \pdfgentounicode=1
\fi

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\pagenumbering{gobble}
\urlstyle{same}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{5pt}{3pt}

\newcommand{\resumeHeader}[1]{%
  \begin{center}
    \vspace{0pt}
    {\fontsize{18pt}{20pt}\selectfont\bfseries #1\par}
    \vspace{0pt}
  \end{center}
}
\newcommand{\role}[4]{\textbf{#1} \hfill #2 \\
\textit{#3} \hfill \textit{#4}\\[-5pt]}

\begin{document}

\resumeHeader{Mutahhar BM - Senior Frontend Engineer}
\begin{center}
\fontsize{9pt}{10pt}\selectfont
\href{mailto:mutahharbinmuzaffar@gmail.com}{mutahharbinmuzaffar@gmail.com} \;|\; +92 301 2498730 \;|\;
\href{https://www.linkedin.com/in/mutahhar-bin-muzaffar}{linkedin.com/in/mutahhar-bin-muzaffar} \;|\;
\href{https://github.com/bmutahhar}{github.com/bmutahhar}
\end{center}

\section*{Summary}
Senior Frontend Engineer with 5+ years of experience building React and Next.js products with JavaScript and TypeScript, with hands-on ownership of architecture, performance optimization, automated testing quality, and cross-functional delivery.

\section*{Experience}
\role{Senior Frontend Engineer}{Jul 2023 -- Present}{\href{https://www.imagine.art/}{\textbf{\underline{ImagineArt}}} - Vyro.ai}{Islamabad, Pakistan}
\begin{itemize}[leftmargin=*, itemsep=0pt, topsep=0pt, partopsep=0pt, parsep=0pt, after=\vspace{1pt}]
  \item Delivered \href{https://www.imagine.art/flow}{\textbf{\underline{Workflows}}} from ideation to MVP launch by defining a unified React Flow architecture for text, image, and video generation.
  \item Scaled team delivery capacity by onboarding and mentoring 4--5 engineers while setting implementation direction for complex real-time node orchestration.
  \item Increased release consistency across microfrontend modules by setting Git workflows and maintaining a Vercel CI/CD pipeline for independently deployed frontend surfaces.
  \item Improved rollout efficiency by 60\% and reduced access-update overhead by 35\% by building subscription gating with Firebase Remote Config and tag-based edge caching.
  \item Improved cross-environment API reliability by resolving CORS and Authorization header mismatches with backend teams across dev, staging, and production.
\end{itemize}

\role{Full Stack Developer}{Mar 2022 -- Mar 2025}{\href{https://www.engiselle.com/}{\textbf{\underline{Engiselle}}}}{Singapore}
\begin{itemize}[leftmargin=*, itemsep=0pt, topsep=0pt, partopsep=0pt, parsep=0pt, after=\vspace{1pt}]
  \item Increased transaction volume by 20\% by delivering production eCommerce products, including an online pharmacy and a home-repair platform.
  \item Increased user engagement by 35\% by implementing real-time event-notification workflows with Socket.io across key product flows.
  \item Improved production stability by deploying backend services on AWS EC2 and managing PostgreSQL on Amazon RDS for application reliability.
  \item Strengthened controlled resource access by configuring Amazon S3 bucket policies and AWS IAM access controls for shared production assets.
\end{itemize}

\role{Software Engineer}{Jun 2022 -- Jun 2023}{\href{https://www.devsinc.com/}{\textbf{\underline{DevsInc}}}}{Islamabad, Pakistan}
\begin{itemize}[leftmargin=*, itemsep=0pt, topsep=0pt, partopsep=0pt, parsep=0pt, after=\vspace{1pt}]
  \item Delivered a healthcare provider dashboard by building React and Material UI scheduling workflows with Twilio video integration for provider-patient coordination.
  \item Improved frontend release confidence by implementing unit tests with Jest and React Testing Library (RTL) across components and feature workflows.
  \item Improved API flexibility for product features by implementing and consuming GraphQL queries and mutations across a React frontend and NestJS backend.
  \item Reduced load time by 40\% and reduced support tickets by 30\% by optimizing dashboard queries and resolving 50+ production issues.
\end{itemize}

\role{Software Engineer}{Oct 2021 -- Jun 2022}{Pakistan Air Force}{Islamabad, Pakistan}
\begin{itemize}[leftmargin=*, itemsep=0pt, topsep=0pt, partopsep=0pt, parsep=0pt, after=\vspace{1pt}]
  \item Reduced deployment time by 50\% while supporting 99.9\% uptime by deploying 20+ Docker images on local Kubernetes for R\&D geospatial systems.
\end{itemize}

\section*{Education}
\textbf{Bachelor of Computer Science} \hfill 2021 \\
COMSATS University, Islamabad \hfill CGPA: 3.73/4.00

\section*{Skills}
\textbf{Languages:} JavaScript, TypeScript, HTML, CSS/SCSS \\
\textbf{Frontend:} React, Next.js, Redux, Zustand, Tailwind CSS, Microfrontend Architecture \\
\textbf{API/Data:} REST APIs, GraphQL, React Query, Data Modeling \\
\textbf{Quality/Delivery:} Jest, React Testing Library, CI/CD (Vercel), Git, Performance Optimization, SSR

\end{document}
